---
title: "LEEF CA planning"
output:
  github_document:
    toc: yes
  html_document:
    toc: yes
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
library(pacman)
pacman::p_load(
  "devtools", 
  "magrittr", 
  "knitr"
)
pacman::p_load_gh(
  "rkrug/plantuml"
)
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  cache = TRUE,
  fig.retina = 4
)
```

# Ideas
- The workflow should be separated from the functionality, i.e. R package containing functionality, scripts (or other packages) which contain the workflow load the functionality package and condtrol the analysis.

- the forecast should be triggered automatically after the data has been updated, thus the forecasts are perfectly in sync with the data. The Forecast repo will contain a link to the tag of the data used for the last release. it would be ideal to have the same tags for Data release and Forecast release.

## Data storage backend

The implementation of the framework should be agnostic to the database backend where the actual data is stored. 
Provessing will be done usinf dplyr and dbplyr.

This from https://rviews.rstudio.com/2017/09/20/dashboards-with-r-and-databases/ gives an impression on what can be done:

***

> This code snippet is an example YAML file that config is able to read. It has one driver name for local development, and a different name for use during deployment:

```{r eval = FALSE, echo = TRUE}
default:
  mssql:
      Driver: "SQL Server"
      Server: "[server's path]"
      Database: "[database name]"
      UID: "[user id]"
      PWD: "[pasword]"
      Port: 1433
rsconnect:
  mssql:
      Driver: "SQLServer"
      Server: "[server's path]"
      Database: "[database name]"
      UID: "[user id]"
      PWD: "[pasword]"
      Port: 1433
```

> The default setting will be automatically used when development, and RStudio Connect will use the rsconnect values when executing this code:

```{r eval = FALSE, echo = TRUE}
dw <- config::get("mssql")
con <- DBI::dbConnect(odbc::odbc(),
                      Driver = dw$Driver,
                      Server = dw$Server,
                      UID    = dw$UID,
                      PWD    = dw$PWD,
                      Port   = dw$Port,
                      Database = dw$Database)

```
                      
***
                      
I am investigating if I can also use csv files as a backend which I hope, as otherwise it needs to be considered adding an sqlite database to the github repo.                      
                    
Smaller databases couyld be located on github (as csv or sqlite databases) and larger ones can be hosted on external database servers. The connection parameters are stored in a config file and define the backend. Therefore, later migration would not be a problem as simply the data needs to migrated and the new location needs to be specified in the config file.
                      
##  DOI archiving via Zenodo **<span style="color:red">TODO</span>**
DOIs will be automatically created through github and the creation of a release. See 
https://zenodo.org/account/settings/github/
and
https://help.github.com/articles/creating-releases/

##  Trusted Timestamps **<span style="color:green">IN PROGRESS</span>**
Trusted Timestamps are automatically created using https://originstamp.org. They are automatically created by using a webhook which is triggered by most events. See https://originstamp.org/dev and particularly https://originstamp.org/dev/git for how to set it up. The email address used at the moment is rainer@krugs.de.

https://www.gipp.com/wp-content/papercite-data/pdf/gipp15a.pdf

https://www.gipp.com/wp-content/papercite-data/pdf/gipp2016a.pdf

### TimeStamps requested from GitHub or from R? If from R, they could be included in the commit
https://www.gwern.net/Timestamping as a way of timestamping individual files, where the resulting references can be included in the commit, as well as a very nice background info on how these things work and can be done locally.

### **<span style="color:red">TODO save seed with TTS hash for manual verifycation</span>**

## **<span style="color:red">TODO</span>** Docker
All processing should be done in docker container to guarantee reproducability. This is especially true for the forecast, but it would be preferable to also do this for the import of the data as this already contains some processing and data cleaning.


## Data Structure
### Which data sources
This determines how many tables (csv files) will be in the database / directory and their content.





## Travis Alternatives regarding `docker`
- https://drone.io/pricing/ it uses directly docker container. Either on own server or subscription
- one could investigate the caching http://atodorov.org/blog/2017/08/07/faster-travis-ci-tests-with-docker-cache/ to make the execution faster
- http://rundef.com/fast-travis-ci-docker-build <span style="color:green"> - interesting option to cache the docker images</span>


# Local Processing
## Current processing

```{r localProcessingCurrent}
'
start
:take samples;
fork
  :Flow Cytometry
  //every second day//;
  :"".c6"" file;
  :R script
  # convert "".c6"" to "".fsa"" using python
  # read "".fsa"" and gates data
  # saves as "".csv"";
fork again
  :Flow CAM
  //every second day//;
  :# images of each particle
  # identification of species using reference image selection
  **This is done internally in a black box**;
  :output of "".csv"" file containi g count of species;
fork again
  :Video / Bemovi
  //every second day//;
  :Video recording;
  :Video Analysis using Bemovi R package
  # classification of identified particles
  #export of each individual (species and size) into "".csv"" file;
fork again
  :Manual Count
  // every second day//;
  :Count of each species;
  :Entering into "".xls"" form incl. data checks;
  :export "".csv"" file;
fork again
  :Respirometer / Tepmperature
  //every second day//;
  :Download of "".csv"" file;
fork again
  :Total Organic Carbon
  //every second day//;
  :Local Processing ?;
  :"".csv"" file for further processing;
fork again
  :Temperature Incubator Log
  //continuous and automatic//;
  :Local Processing ?;
  :"".csv"" file for further processing;
end fork
:create new branch on Data Repo Fork;
:commit new data;
:push to github;
:issue pull request to Data Repo;
' %>%
  plantuml %>%
  plot
```


All file sizes are per sample.

### Flow Cytometry

1. Machine output `.c6`
2. R script 
    1. python (anaconda) command for conversion of `.c6` to `.fca`.
    2. `BioBase` package reads `.fca` into R, and 
    3. further processing and gating by using `flowCore`
    4. results in `.csv` with count of particles of gated dataset

#### File Size
- **raw data (`.c6`):** $100 \dots 200MB$
- **final data (`.csv`):**  $1 \dots 2MB$

#### **<span style="color:red">TODO</span>** 
- convert R script into package
- is it usefull to archive `.c6` or file or the one converted to `.fca`? Large storage space requirements!!!!


### Flow CAM
1. input of reference images for identification
2. automated classification of particles using reference images
3. output `.csv` with count of each species


#### File Size
- **raw data (`.IMAGE`):** a lot
- **final data (`.csv`):**  $<1MB$

#### **<span style="color:red">TODO</span>**
- The image classification of the particles into species is done by the Flow CAM. Would it be usefull to do the classifiaction externally (reproducability?)? In this case, the same algorythms as for the Bemovi particle identification could be used.

### Video / BeMovie
1. input of reference images for identification
1. video recording (**~500MB**)
2. Video analysis using `Bemovi` R package
3. classification of particles into species
4. results in `.csv` file with size info for each individual particle identified
5. can be aggregated to return only mean sizes, but not ideal as aggregated

#### File Size
- **raw data (`.VIDEO`):** $500MB$
- **final data (`.csv`):**  $<1MB$

#### **<span style="color:red">TODO</span>**
- testig quality of recording. The testing of the movie should be done in Bemovi itself (add to package possibly?)
  1. processing of first seconds of the video
  2. automatic recognition of errors / quality
  3. assign quality value ($1 \dots 0$) 
  4. depending on threshold continue processing, request re-recording, or ask for confirmation from operator
- analyse whole movie

### Manual Count
1. count individuals
2. `.csv` file with count of individuals in each species and dilution 

#### File Size
- **raw data (`.xls`):** $<1MB$
- **final data (`.csv`):**  $<1MB$

#### **<span style="color:red">TODO</span>**
- design excel form (or similar) to make data entry safer and include initial checks

#### Processing to be done

### Respirometer and Temperture
1. results in `.csv` file with info on $O_2$ and temperature

#### File Size
- **raw data (`.csv`):** $<1MB$
- **final data (`.csv`):**  $<1MB$

#### **<span style="color:red">TODO</span>**
- nothing I am aware of

### Total Organic Carbon
Need info from Yves.

#### File Size

- **raw data (`.csv`):** $<1MB$
- **final data (`.csv`):**  $<1MB$

#### **<span style="color:red">TODO</span>**

### Temperature Incubator Log
1. continuouslog file - format?

#### File Size

- **raw data (`.???`):** $???$
- **final data (`.csv`):**  $???$

#### **<span style="color:red">TODO</span>**
- nothing I am aware of


# Sequence Diagrams
## Overview
```{r seq_overview}
'
entity Experiment as exp
actor Local as lpr
database github as ghb
control Travis as trv
collections RPackages as rpk

exp -> lpr : generates data
== Local Processing ==
lpr -> lpr : data processing
lpr -> ghb : pushes data (pullrequest?)
== cloud processing ==
ghb -> trv : requests data cleaning
activate trv
trv <- rpk : loads packages
trv -> ghb : returns cleaned data
deactivate trv
ghb -> trv : requests publishing of data
activate trv
trv <- rpk : loads packages
trv -> ghb : publishes data
deactivate trv
ghb -> trv : requests forecasts
activate trv
trv <- rpk : loads packages
trv -> ghb : publishes data
deactivate trv
ghb -> trv : requests publishing of forecasts
activate trv
trv <- rpk : loads packages
trv -> ghb : publishes forecasts
deactivate trv
' %>%
  plantuml %>%
  plot
```


## Master Repos
```{r sequence_detailed_main_repo, eval = TRUE, results = "asis"}
'
entity Experiment as exp
actor Local as lpr
box "Github"
  database "fork of LEEF.Data.Master" as ghbr #red
  database "LEEF.Data.Master" as ghbd #red
  database "LEEF.Forecast.Master" as ghbf #red
  database "LEEF.Data.Child" as ghbdp #green
end box
control Travis as trv
box "R Packages"
  collections LEEF.Processing as rdc
  collections LEEF.Forecasting as rfc
  collections LEEF.Publishing as rpb
end box

control OriginStamp as os

== LEEF Experiment ==

exp -> lpr : generates data

== Local Processing ==

lpr -> lpr : data cleaning
lpr -> lpr : data processing
lpr -> ghbr : commits data to new branch

== cloud processing ==
ghbr -[#red]> ghbd : pull request

ghbd -[#red]> trv : initiates data import
activate trv
group import new data
  trv <- ghbd : loads Data package
  trv <- rdc : loads Data Processing package
  group import
      trv -> trv : data checks using unit testthat
      trv -> trv : data cleaning
      trv -> trv : if successfull, collect data in folder `/inst/new_data/checked`
      group Trusted Time Stamping
        ghbd -> os : request timestamp for files in `/inst/new_data/checked` 
        os -> lpr : sends timestamp confirmation after submission to Bitcoin Blockchain
        trv -> trv : adds timestamp hash to folder `/inst/new_data/checked`
      end
      trv -[#red]> ghbd : if successfull, commit data and timestamp in `/inst/new_data/checked` folder for appending
      group Trusted Time Stamping
        ghbd -> os : request timestamp for commit via github webhook
        os -> lpr : sends timestamp confirmation after submission to Bitcoin Blockchain
      end
      trv -> lpr : Report back
  end

  group publish
      trv <- rpb : loads Publishing package
      trv -[#red]> ghbd : publishes data
  end

  group update child repos (public data)
    trv -> trv : filter data for child repo (embargoed data out)
    trv -[#green]> ghbdp : commit data for archiving
  end
  trv -[#red]> ghbf : requests forecasts by committing REQUEST_FORECAST token
  deactivate trv
end

ghbf -[#red]> trv : initiates forecasts
activate trv
group forecast
  group forecast
      trv <- rfc : loads Forecast package
      ghbd -[#red]> trv : reads data
      trv -> trv : makes forecasts
      trv -[#red]> ghbf : commit forecasts for archiving
      group Trusted Time Stamping
        ghbf -> os : request timestamp for commit via github webhook
        os -> lpr : sends timestamp confirmation after submission to Bitcoin Blockchain
      end

  end

  group publish
      trv <- rpb : loads Publishing package
      trv -[#red]> ghbf : publishes forecasts
    deactivate trv
  end
end

' %>%
  plantuml %>%
  plot
```

## Child Repos (public)
```{r sequence_detailed_child_repo, eval = TRUE, results = "asis"}
'
actor Local as lpr

box "Github"
  database "LEEF.Data.public" as ghbdp #green
  database "LEEF.Forecast.public" as ghbfp #green
end box
control Travis as trv
box "R Packages"
  collections LEEF.Processing as rdc
  collections LEEF.Forecasting as rfc
  collections LEEF.Publishing as rpb
end box

control OriginStamp as os
control Zenodo as doi

== cloud processing ==
activate trv
    trv -[#green]> ghbdp : commit data for archiving
deactivate trv


ghbdp -[#green]> trv : initiates data import
activate trv
trv <- rdc : loads Data Processing package
group import new data
  group import
      trv -[#green]> ghbdp : commit data for archiving
      group Trusted Time Stamping
        ghbdp -> os : request timestamp for commit via github webhook
        os -> lpr : sends timestamp confirmation after submission to Bitcoin Blockchain
      end
      group DOI
        ghbdp -> doi : request DOI for commit via github webhook
        os -> lpr : sends DOI confirmation
      end
      trv -> lpr : Report back
  end

  group publish
      trv <- rpb : loads Publishing package
      trv -[#green]> ghbdp : publishes data
  end

  trv -[#green]> ghbfp : requests forecasts by committing REQUEST_FORECAST token
  deactivate trv
end

ghbfp -[#green]> trv : initiates forecasts
activate trv
group forecast
  group forecast
      trv <- rfc : loads Forecast package
      ghbdp -[#green]> trv : reads data
      trv -> trv : makes forecasts
      trv -[#green]> ghbfp : commit forecasts for archiving
      group Trusted Time Stamping
        ghbfp -> os : request timestamp for commit via github webhook
        os -> lpr : sends timestamp confirmation after submission to Bitcoin Blockchain
      end
      group DOI
        ghbfp -> doi : request DOI for commit via github webhook
        os -> lpr : sends DOI confirmation
      end
  end

  group publish
      trv <- rpb : loads Publishing package
      trv -[#green]> ghbfp : publishes forecasts
    deactivate trv
  end
end
' %>%
  plantuml %>%
  plot
```

### Remarks
#### DOI and TrustedTimeStamp
These need to be enabled in the repo itself via webhooks. Alternatively, one could also call them from R via a `curl` command - advantages would be more control?


#### config file in repo which specifies properties
Format has to be human readable, YAML and one can use the package `config` https://cran.r-project.org/web/packages/config/ to load the configs easily. Also, one can specify the configuration for Master as well as Child repo in one config file which can be in all repos of the set.

Possible fields (with default valuse) could be (if one is using R instead of webhooks for DOI and TTS):
```{r, echo = TRUE, eval = FALSE}
default:
  doi: FALSE
  tts: TRUE
  data:
    backend: 
    
master:
  doi: FALSE
  tts: TRUE
  data:
    backend:
      mssql:
        Database: "[database name]"
        UID: "[user id]"
        PWD: "[pasword]"
        Port: 1433
        
public:
  doi: TRUE
  tts: TRUE
  data:
    backend:
      csv:
        folder: rawData 

heatwave_e_1:
  doi: TRUE
  tts: TRUE
  data:
    backend:
      csv:
        folder: rawData 
  
heatwave:
  doi: FALSE
  tts: TRUE
  data:
    backend:
      mysql:
        Database: "[database name]"
        UID: "[user id]"
        PWD: "[pasword]"
```

In addition, the repo will contain one file named CONFIG_NAME which contains the name of the config to be used, e.g. `master` if it is the nmaster config

### Questions
- How to deal with embargoed data - date for end embargo? 
    - **Problem**: What if embargo date changes? SHould we change already older data? I don't like this.
    - **Better**: column for embargo id, where each id will be specified in meta data table, in which the final date for embargo is stored. So the actual data does not need to be changed later if the embargo needs to be extended, only the embargo table needs to be changed
- mor than one level of child repos necessary? I don't think so.
   

#### Data table
 data  | child repo key    |
------ | --------------- |
 ...   | public_MSC_Peter |
 ...   | public_PhD_Mary |
 ...   | heatwave_private |
 ...   | heatwave |
 
Do we need multiple child repos? Should be easy to implement and adds flexibility.

#### Child Repo Table
If there are not to may, a YAML config file could be used, otherwise a table. The YAML file would be easier to edit.
##### Table

child repo key | child repo              | from        | until      |
--- | --- | --- | --- |
public_MSC_Peter | LEEF.Data.public      | 12.05.2019  |            |
public_PhD_Mary | LEEF.Data.public       | 12.05.2022  |            |
heatwave_e_1 | LEEF.Data.heatwave.public | 01.01.2019  | 01.01.2019 |
heatwave_private | LEEF.Data.heatwave    | 01.01.2018  | 01.01.2020 |
    
##### YAML file
```{r echo = TRUE, eval = FALSE}
public_MSC_Peter:
    from:  12.05.2019
    until:
    repo: LEEF.Data.public
public_PhD_Mary:
    from:  12.05.2022`
    until:
    repo: LEEF.Data.public
heatwave_e_1:
    from:  01.01.2019
    until: 01.03.2019
    repo: LEEF.Data.heatwave.public
heatwave_private:
    from:  01.01.2018
    until: 01.01.2020
    repo: LEEF.Data.heatwave
```

# Activity Diagrams

## Import new data
```{r activity_import, eval = TRUE, results = "asis"}
'
start

:**pull request**
to import new data;

:load Data Processing Package
""library("LEEF.Processing")"";

if (existing dataset correct\n""existingDataOK()"") then (""FALSE"")
  :send detailed report of error;
  :abort processing;
  stop
elseif (new data correct\n""newDataOK()"") then (""FALSE"")
  :send detailed report of error;
  :abort processing;
  stop
else 
  :import data\n""importData()"";

if (new dataset correct\n""existingDataOK()"") then (""FALSE"")
  :abort processing;
  :send detailed report of error;
  stop
else 

  :update version;

  :load Data Publishing Package
  ""library("LEEF.Publishing")"";

  partition "update Master Data" {  
    :update package data
    ""updatePackageData()"";

    :commit new dataset to Data repo
    using username only for these updates;
    :get trusted timestamp of hash of last commit
    automatically via webhook originstamp.org;
    :create new version tag;
    :get trusted timestamp of last tag
    automatically via webhook originstamp.org;
    :create release;
    :commits NEW_DATA file to Forecast repo
    repo initiates forecasts;

    :publish data to website
    initially ""doc"" directory in Data repo
    ""publishData()"";
  }
  partition "send data to child repos" {
    :=read child repos as listed in ""CHILD_REPOS.txt"";
    repeat
      :pull child Data repo;
      :select data points for child Data repo
      ""selectChildRepoData(childRepo)"";
      :add new data to child Data repo;
      :**commit** data to child Data repo
      Commit triggers **Import new Data** in child Data repo;
    repeat while (for all child repos)
  }

  end
' %>%
  plantuml %>%
  plot
```


### Check existing data (`existingDataOK()`)
### Check new data (`newDataOK()`
### Import Data (`importData()`
### Publish Data (`publishData()`)

## Forecast
```{r activity_forecast, eval = TRUE, results = "asis"}
'
start

:**commit**;

:load Forecast Package
""library("LEEF.Forecast")"";

if (is request for forecast\n""isForecastRequest()"") then (""FALSE"")
  end
else
  :clone Data repo;
  
if (new dataset suitable for forecast\n""dataForForecastOK()"") then (""FALSE"")
  :send detailed report of error;
  stop
else 
  partition """calcAllModels()""" {
    repeat
      :process next model plugin
      ""calcModel(model)"";
      :save results of forecast;
    repeat while (more model plugins?)
  }

  :calculate meta models\n""calcMetaModels()"";

  :update package data
  ""updatePackageData()""
  :set reference to Data version and repo;
  :update version;
  :commit new data to Forecast repo
  using username only for these updates;
  :get trusted timestamp of hash of last commit
  automatically via webhook originstamp.org;
  :create new version tag;
  :get trusted timestamp of last tag
  automatically via webhook originstamp.org;
  :create release
  requests new DOI for this release;
  
  :load Data Publishing Package
  ""library("LEEF.Publishing")"";

  :publish data to website
  initially ""doc"" directory in Forecast repo
  ""publishForecast()"";
  end
' %>%
  plantuml %>%
  plot
```

# Component Diagrams
```{r com_plantuml, eval = FALSE}
'
package "LEEF Experiment" {
  [Environmental variables] as ev
  [Microbial Communities Data] as mcd
  ev <..> mcd
}

package "Local" {
  [Data Preparation] as dpl
}

cloud  "Cloud - processing" {

  database "github --- Master" {
    folder "Master" {
      [Data Archiving] as dar
    }

    folder "Public" {
      [Data] as data
      [Forecasts] as for
    }
  }

  database "github --- packages" {
    [LEEF_RawData] as rdp
    [LEEF_Forecast] as rfc
    [LEEF_Publish] as rpb
    }

  database "Travis" {
    [Data Preparation] as dpr
    [Data Pubvlishing] as dpb
  }

ev --> dpl
mcd --> dpl

dpl --> dar : pushed

dar --> dpr : requests data preparation
dpr <-- rdp : loads R package
dpr --> dar : returns data for archiving

dar --> dpr : requests data preparation
dpr <-- rdp : loads R package
dpr --> dar : returns data for archiving

dar --> dpb : requests data preparation
dpb <-- rpb : loads R package
dpb --> data : returns data for archiving


}
' %>%
  plantuml %>%
  plot
```


# Github Repos
Github repos are used to archive the data and the forecasts. They also host the R packege which containe the functionality, but here I will focus on the Data github repos.


## Private
We need some private repos, as some data will be embargoed for some time due to thesis and publication priorities.

### LEEF
Repo comntaining this document and all information about the other repos and links.

#### GitHub apps
- Trusted Timestamp for all transactions

### LEEF.Data.Master
This repo is used for archiving all data. It will contain the checked and cleaned data. Functions from the Publishing R package can be used to calculate summary stats and show these on a website.

The repo is structured as an R package which contains all the data. In addition, the data is stored in a csv format in the `rawData` folder for access from other programs. The easiest way to get the updated data is to update the package in R.


#### GitHub apps
This repo, when receiving a pull request, triggers a Travis-ci build to
- check the data contained in the pull request
- clean the data contained in the pull request
- update the data in the repo if the data is OK and cleaned successfully via a commit as new version.
- Trusted Timestamp for all transactions
- publishibng of public data to public repo
- after updating, forecasting is triggered

### Forecasts Archiving
- get updated data from Archive
- calculate forecasts
- archive forecasts as new version
- publishibng of forecasts based on public data to public repo
- Get DOI?

#### GitHub apps
- Travis-ci to do the forecasts and update the repo afterwards

## Public
### Data Archiving
#### GitHub apps
### Forecasts Archiving
#### GitHub apps

# Database Modelling **<span style="color:red">TODO</span>**
Layout Based on https://gist.github.com/QuantumGhost/0955a45383a0b6c0bc24f9654b3cb561

```{r databaseModell, eval = FALSE}
'
skinparam dpi 300
!define Table(name,desc) class name as "desc" << (T,#FFAAAA) >>
\' we use bold for primary key
\' green color for unique
\' and underscore for not_null
!define primary_key(x) <b>x</b>
!define unique(x) <color:green>x</color>
!define not_null(x) <u>x</u>
!define field(x) <color:black>x</color>
\' other tags available:
\' <i></i>
\' <back:COLOR></color>, where color is a color name or html color code
\' (#FFAACC)
\' see: http://plantuml.com/classes.html#More
hide methods
hide stereotypes

\' entities

Table(user, "user (User in our system)") {
primary_key(id) INTEGER
not_null(unique(username)) VARCHAR[32]
not_null(password) VARCHAR[64]
}

Table(session, "session (session for user)") {
primary_key(id) INTEGER
not_null(user_id) INTEGER
not_null(unique(session_id) VARCHAR[64]
}

Table(user_profile, "user_profile (Some info of user)") {
primary_key(user_id) INTEGER
age SMALLINT
gender SMALLINT
birthday DATETIME
}

Table(group, "group (group of users)") {
primary_key(id) INTEGER
not_null(name) VARCHAR[32]
}

Table(user_group, "user_group (relationship of user and group)") {
primary_key(user_id) INTEGER
primary_key(group_id) INTEGER
joined_at DATETIME
}

\' relationships
\' one-to-one relationship
user -- user_profile : "A user only has one profile"
\' one to may relationship
user --> session : "A user may have many sessions"
\' many to many relationship
\' Add mark if you like
user "1" --> "*" user_group : "A user may be in many groups"
group "1" --> "0..N" user_group : "A group may contain many users"
' %>%
  plantuml %>%
  plot
```
# R Packages

## Data
## Data Check and Cleaning
See the LEEF.Processing package

## Forecast
- Interface for models needs to be defined
    - data structure (S3 methods) for input and putput data
- models in separate packages preferable


```{r leef.forecast}
'
package "LEEF.forecast" {
  class "Unit Check" << (G,#FF7700) >> {
  }
  class "Data Check" << (G,#FF7700) >> {
    + isForecastRequest()
    + dataForForecastOK()
  }
  class "Plugin infrastructure" << (G,#FF7700) >> {
    + calcAllModels()
    + calcModels()
    + calcMetaModels()
    + newForecastInputData()
    + newForecastOutputData()
    + updatePackageData()
  }
  class "ForecastInputData" << (S,#FF7700) "S3 Class" >> {
    + ToBeDefined
  }
  class "ForecastOutputData" << (S,#FF7700) "S3 Class" >> {
    + ToBeDefined
  }
}
' %>%
  plantuml %>%
  plot
```

## Publish
```{r leef.publish}
'
package "LEEF.Publish" {
  class "Unit Check" << (G,#FF7700) >> {
  }
  class "Publishing" << (G,#FF7700) >> {
    + publishData()
    + publishForecast()
  }
}
' %>%
  plantuml %>%
  plot
```


# Background info
- Commits have to be signed and contain a trusted timestamp, e.g. 
    - https://proofofexistence.com/
    - https://tsa.safecreative.org/
    - https://www.freetsa.org/index_en.php
    - this one looks promising: https://www.npmjs.com/package/gitlock
    - Some background to Trusted Timestamps https://d-mueller.de/blog/dealing-with-trusted-timestamps-in-php-rfc-3161/
    - bitcoin blockchain https://www.ideals.illinois.edu/bitstream/handle/2142/73770/478_ready.pdf
    - https://github.com/cgwalters/git-evtag ?
