---
title: "02 Local Pipeline Management"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{02 Local Pipeline Management}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LEEF)
```

# Background

The repository [local_pipeline_management](https://github.com/LEEF-UZH/local_pipeline_management) in the [LEEF-UZH organisation](https://github.com/LEEF-UZH) on github contains the bash functions to manage the pipeline remotely. These commands do run in the Linux terminal as well as in the Mac terminals. <span style="color:red">check with windows!!!</span>

To use these commands, you can either [download](https://github.com/LEEF-UZH/local_pipeline_management/archive/main.zip) the repository and unzip it somewhere, or clone the repository using git. This is slightly more complicated, but makes it easier to update the local commands from the github repo.

To clone the commands do the following:

```bash
git clone git@github.com:LEEF-UZH/local_pipeline_management.git
```

which will create a directory called `local_pipeline_management`. When downloading the zip file, you have to extract it, which will create a directory called `local_pipeline_management-main`. The content of these two directories are identical for the further discussion here.

Inside this directory is a directory called `bin` which contains the scripts to manage the pipeline remotely. The commands are:

- `server`
- `upload`
- `prepare`
- `start`
- `status`
- `download`
- `clean`

To execute these commands, you have to be either in the directory where the commands are located, or the directory has to be in the path. If they are not in the path, you have to prepend `./` to the command to work, e.g. `./upload -h` instead of `upload -h` when they are in the path. For thiis tutorial, I will put them in the path.

All commands contain a basic usage help, which can be called by using the `-h` or `--help` argument as in e.g. `./upload -h`. 

```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
upload -h
```

We will now go through the commands available and explain what they are doing and how they can be used. Finally, we will show a basic workflow on how to upload data, start the server, download results, and prepare the pipeline server for the next run.

## The commands

# `server`

## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
server -h
```

## Description
The command `server` returns the adress of the pipeline server. When the adress of the pipeline server changes, you can open the script in a text editor and simply replace the adress in the last line with the new adress.

```{bash echo=FALSE}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
cat $(which server )
```


## Example of typical usage
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
server
```


# `upload`
## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
upload -h
```

## Description

This command uplaods data to the pipeline server. The most common usage is to uplad the data for the pipeline server. This is done by specifying the directory **in which the `00.general.parameter` and `0.raw.data` directory** resides locally.

The copying could also be done by mounting the `leef_data` as a samba share, but it would be slower.

## Example of typical usage

```{bash, eval = FALSE}
upload ./20210101
```

would upload the folder `./20210101` into the folder `Incoming` on the pipeline server.

# `prepare`
## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
prepare -h
```

## Description

Copying the data from within the folder `from` in the `LEEF` folder where it can be processed by the pipeline. Before copying the data, folder leftovers from earlier pipeline runs are dewleted by running the `clean` script. 

## Example of typical usage

```{bash, eval = FALSE}
prepare 20210101
```

# `start`
## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
start -h
```

## Description

The pipeline consists of two actual pipelines, namely one for bemovi (called `bemovi`), which runs several hours, and one for the other measurements (called `fast`), which runs for less than an hour. The typical usage is to run both pipelines (first `fast`, and afterwards `bemovi`).

## Example of typical usage

```{bash, eval = FALSE}
start all
```

# `status`
## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
status -h
```

## Description

The status returned, is the status when the pipeline is started using `start`. When started manually from the pipeline server (or via ssh), the `status` will not be reported correctly. 

## Example of typical usage

```{bash, eval = FALSE}
status
```

# `download`
## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
download -h
```

## Description

Download files or folder from the `LEEF` directory on the pipeline server. If you want to download files from other folders, use `..` to move one directory up. For example, `../Incoming` would download the whole `Incoming` directory.

## Example of typical usage
```{bash, eval = FALSE}
download 9.backend
```

# `clean`
## Help
```{bash}
export PATH=~/Documents_Local/git/LEEF/local_pipeline_management/bin/:$PATH
##
clean -h
```

## Description

Delete all raw data and results folders from the pipeline. The folders containing the archived data as well as the backend (containing the Reserch Read Data databases) are not deleted!

This script is run automatically the script `prepare` is executed.

The script asks for confirmation before deleting anything!

## Example of typical usage

```{bash, eval = FALSE}
clean
```



